---
  output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

  ```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```


[![Travis-CI Build Status](https://travis-ci.org/karchjd/gppm.svg?branch=master)](https://travis-ci.org/karchjd/gppm)
<!-- [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ggplot2)](https://cran.r-project.org/package=ggplot2)-->
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/karchjd/gppm?branch=master&svg=true)](https://ci.appveyor.com/project/karchjd/gppm)

## Overview

gppm is an implementation of Gaussian process panel modeling.

## Installation

```{r, eval = FALSE}
devtools::install_github('karchjd/gppm')
```

## Examples

For examples, consult the demos. To see a list of all demos do the following:
```{r}
demo(package='gppm')
```

To run a particular example, you can do the following. Here, exemplified for 'example1linearModel':
```{r, eval=FALSE}
demo('example1linearModel',package='gppm')
```

However, the recommended approach is to look at the source directly. To locate the demo folder in which all examples resides on your computer, do the following:
```{r}
system.file("demo", package ="gppm")
```

## Learning Gaussian Process Panel Modeling

This [dissertation][diss] and this [paper][pap] describe the method.

## Getting help

Send an email to j.d.karch@fsw.leidenuniv.nl.

[diss]: https://edoc.hu-berlin.de/handle/18452/18293
[pap]: https://psyarxiv.com/kvw5y/
