---
  output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```


  <!-- badges: start -->
  [![R-CMD-check](https://github.com/karchjd/gppm/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/karchjd/gppm/actions/workflows/R-CMD-check.yaml)
  [![Codecov test coverage](https://codecov.io/gh/karchjd/gppm/graph/badge.svg)](https://app.codecov.io/gh/karchjd/gppm)
  <!-- badges: end -->

## Overview

gppm is an implementation of Gaussian process panel modeling.

## Installation

```{r, eval = FALSE}
devtools::install_github("karchjd/gppm")
```

## Examples

For examples, consult the demos. To see a list of all demos do the following:
```{r}
demo(package = "gppm")
```

To run a particular example, you can do the following. Here, exemplified for 'example1linearModel':
```{r, eval=FALSE}
demo("example1linearModel", package = "gppm")
```

However, the recommended approach is to look at the source directly. To locate the demo folder in which all examples resides on your computer, do the following:
```{r}
system.file("demo", package = "gppm")
```

## Learning Gaussian Process Panel Modeling

This [dissertation][diss] and this [paper][pap] describe the method.

## Getting help

Send an email to j.d.karch@fsw.leidenuniv.nl.

[diss]: https://edoc.hu-berlin.de/handle/18452/18293
[pap]: https://www.frontiersin.org/journals/psychology/articles/10.3389/fpsyg.2020.00351/full
